Turtlebot SLAM

### 2013-01-22 trunk/Article/Article.tex
Small error corrected.
Occupancy grid corrected.

The methods explained in this sections are implemented in the object-oriented programming language C++. The code is specifically designed for the ROS environment (see Subsection \ref{subsec:ros}). The installation process for ROS, as performed for this paper, can be reviewed on \cite{swarmlab}.

@@

The occupancy grid is a structure that is represented by a one-dimensional array. The size of an occupancy grid has to be tuned problem specific. A too large grid can lead to performance problems. If the grid is too small, however, the map will be inaccurate. Fitting a map on a smaller grid results in a low resolution.
Internally the program represents the grid as a two dimensional array. This makes navigating to either side more intuitive. Each grid cell contains an integer value. The value-range for ROS' occupancy grid lies between $-1$ and $100$ \cite{occupancy}. The values indicate the state as follows:
\begin{description}
\item{$-1$} : Unknown space, not yet covered by robot's perception sensors
\item{$0$} : Known free space, robot can drive on it safely
\item{$1-100$} : Probability of being an obstacle, $1$ being a low probability and $100$ being a definite obstacle.
\end{description}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.45\textwidth]{figures/Occup.png}
	\caption{A visualized occupancy grid}
	\label{fig:Occupancy}
\end{figure}
Figure \ref{fig:Occupancy} shows an example occupancy grid. The robot stands in the center of the it. It senses the state of all cells within a distance of one. The border cells are marked with a $-1$, which means that they are still unexplored. The remaining cells are explored being either an obstacle (100) or free space (0).
The occupancy grid is created using laser scan data. Each laser scan contains information about whether or not an obstacle has been detected at a certain bearing. Maximum range readings occur when the robot senses only free space in a certain direction. All laser scans are transformed into point clouds. The absolute locations of the points are dependent on the pose at which the laser scan was recorded.
In the occupancy grid detected obstacle points are indicated by a value of 100.
Free space is being incorporated into the map by filling regions between detected points and the concerning robot position.

>>>>

The methods explained in this section are implemented in the object-oriented programming language C++. The code is specifically designed for the ROS environment (see Subsection \ref{subsec:ros}). The installation process for ROS, as performed for this paper, can be reviewed on \cite{swarmlab}.

@@

The occupancy grid is a structure that is represented by a one-dimensional array. The size of an occupancy grid has to be tuned problem specific. A too large grid can lead to performance problems. If the grid is too small, however, the map will be inaccurate. Fitting a map on a smaller grid results in a low resolution.
Internally the program represents the grid as a two dimensional array. This makes navigating to either side more intuitive. Each grid cell contains an integer value. The value-range for ROS' occupancy grid lies between $-1$ and $100$ \cite{occupancy}. The values indicate the state as follows:
\begin{description}
\item{$-1$} : Unknown space, not yet covered by robot's perception sensors
\item{$0$} : Known free space, robot can drive on it safely
\item{$1-100$} : Probability of being an obstacle, $1$ being a low probability and $100$ being a definite obstacle.
\end{description}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.45\textwidth]{figures/Occup.png}
	\caption{A visualized occupancy grid}
	\label{fig:Occupancy}
\end{figure}
Figure \ref{fig:Occupancy} shows an example occupancy grid. The robot stands in the center of it and makes one measurement consisting of several laser scans. Each scan returns the range it was able to reach. The returned range is either the maximally possible range of the laser or a lower value, indicating an obstacle (value of 100). The range is transformed into global coordinates with respect to the robot's location, orientation and the bearing of the laser beam. The resulting point is then transferred into the occupancy grid as an obstacle if the maximum range was not reached. The cells lying in a straight line between the transformed range and the robot are considered free space (value of 0), since the laser was able to pass through this area. All the cells that are not affected by any of the previous steps remain unexplored (value of -1). Naturally, this is the case for cells behind obstacles, out of range and directly behind the robot.
